Simulation Summary Figures

### 2018-09-06 datasets/simulations/simulations-summary.Rmd
Update sim summary Rmd based on renamed/moved simulation settings

resmet <- dplyr::mutate(resmet, pi0 = ifelse(grepl("varyingpi0", setting), dist, 90))
resmet <- dplyr::mutate(resmet, pi0 = as.numeric(gsub("nullprop", "", pi0)))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("varyingpi0", setting), "gaussian", dist))

resmet <- dplyr::mutate(resmet, signal = ifelse(grepl("varyinges", setting), dist, NA))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges$", setting), "gaussian", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges-t$", setting), "t11", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges-chisq$", setting), "chisq4", dist))
resmet <- dplyr::mutate(resmet, setting = ifelse(grepl("varyinges", setting), "varyinges", setting))

@@

We also replace the sampling noise labels with more plotting-friendly labels.

```{r}
resmet <- dplyr::mutate(resmet, dist = factor(dist, levels = c("gaussian", "t11", "t5", "chisq4"),
                                              labels = c(expression("Noise: " * N(0, 1)),
                                                         expression("Noise: " * t[11]),
                                                         expression("Noise: " * t[5]),
                                                         expression("Noise: " * {chi^2}[4]))))
```

@@

We take a look at the impact of the informativeness of a covariate on the performance
of the different methods under just the normal sampling noise setting. Here, the informative
covariate is sampled uniformly between 0 and 1 and the probability of the corresponding test
being null is one value if the covariate is less than 0.8, and another value if the covariate
is above 0.8. The "informativeness" is measured by the difference between these two probabilities,
with informativeness 0 and 1 corresponding to no difference and maximal difference (i.e. 0 and 1),
respectively. We plot the false discovery proportion and true positive rate at a nominal alpha
cutoff of 0.05 for each method.

```{r, fig.width = 10, fig.height = 4}
res_info <- dplyr::filter(resmet, setting == "varyinginfo", alpha == 0.05)

@@

```{r, fig.width = 18, fig.height = 8}
res_ua <- dplyr::filter(resmet, setting == "varyinges", grepl("N\\(0, 1\\)", dist))

@@

```{r, fig.width = 18, fig.height = 8}
res_ua <- dplyr::filter(resmet, setting == "varyinges", grepl("t\\[11\\]", dist))

>>>>

resmet <- dplyr::mutate(resmet, pi0 = ifelse(grepl("varyingpi0", setting), dist, 90))
resmet <- dplyr::mutate(resmet, pi0 = as.numeric(gsub("nullprop", "", pi0)))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyingpi0$", setting), "gaussian", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyingpi0-t$", setting), "t11", dist))

resmet <- dplyr::mutate(resmet, signal = ifelse(grepl("uasettings", setting), dist, NA))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^uasettings$", setting), "gaussian", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^uasettings-t$", setting), "t11", dist))
resmet <- dplyr::mutate(resmet, setting = ifelse(grepl("uasettings", setting), "uasettings", setting))

@@

We also replace the test statistic distribution labels with more plotting-friendly labels.

```{r}
resmet <- dplyr::mutate(resmet, dist = factor(dist, levels = c("gaussian", "t11", "t5", "chisq4"),
                                              labels = c(expression("Distribution: " * N(0, 1)),
                                                         expression("Distribution: " * t[11]),
                                                         expression("Distribution: " * t[5]),
                                                         expression("Distribution: " * {chi^2}[4]))))
```

@@

We take a look at the impact of the informativeness of a covariate on the performance
of the different methods under just the normal sampling noise setting. Here, the informative
covariate is sampled uniformly between 0 and 1 and the probability of the corresponding test
being null is more or less dependent on the value of the covariate. The "informativeness" is
greater when the value of the covariate is more informative of the probability of null being
high or low. We plot the false discovery proportion and true positive rate at a nominal alpha
cutoff of 0.05 for each method.

```{r, fig.width = 10, fig.height = 4}
res_info <- dplyr::filter(resmet, setting == "varyinginfo-smooth", alpha == 0.05)

@@

```{r, fig.width = 18, fig.height = 8}
res_ua <- dplyr::filter(resmet, setting == "uasettings", grepl("N\\(0, 1\\)", dist))

@@

```{r, fig.width = 18, fig.height = 8}
res_ua <- dplyr::filter(resmet, setting == "uasettings", grepl("t\\[11\\]", dist))
